---
title: "SimpLin: Simple linear regression"
author: Seongwon Im, CSU
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{SLR}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

$\texttt{SimpLin}$ package performs a simple linear regression faster than the original $\texttt{lm()}$ function in R. The package contains a function, $\texttt{simp_lin_R()}$, which takes two numeric vectors which represent the predictor, $X$ and the response variable, $Y$. 

$$y_i = \beta_0 + \beta_1 x_i + \epsilon_i$$
```{r setup}
library(SimpLin)
```

Here, we take 20 data points which are standard normally distributed as an example for a fit.
```{r}
# Get a randomized exemplary data
x = rnorm(n = 20, mean = 0, sd = 1)
y = rnorm(n = 20, mean = 0, sd = 1)
```

The $\texttt{simp_lin_R()}$ function returns several fundamental values for the linear regression. These values include the estimated $\beta_0$ and $\beta_1$, their standard errors, 95% confidence intervals, predicted values and the residuals.
```{r}
# Fit the model with the simp_lin_R function
fit = simp_lin_R(x, y)

# Estimated coefficients
fit$Coefficients

# Standard Errors
fit$StandardError

# 95% confidence intervals for both b0 and b1
fit$b0_95CI
fit$b1_95CI
```

The function also returns the predicted(Fitted) values and the residuals calculated as shown below.
$$i\text{th predicted value: }\hat{y_i} = \hat{\beta_0} + \hat{\beta_1}x_i$$
$$i\text{th residual: } y - \hat{y_i}$$
```{r}
# Predicted(Fitted)
fit$Predicted

# Residuals
fit$Residuals
```

